---
title: Checking URLs for UK Higher Education Institution Research Data Management
  Policies, 2009-2016
author: "Laurence Horton"
date: "02/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Load packages
```{r packages}
library(tidyverse)
```

Get the data
```{r get data}
policies <-
  read.csv(
    "https://reshare.ukdataservice.ac.uk/852487/8/ukhei-rdmpolicies-2016-10-quant.csv"
  ) # read in spreadsheet
urls <- as.character(policies$hyperlink) # Just keep the URL column.
```

Function to test URLs
```{r function for testing URLs}
url_works <- function(url_in, t = 2) {
  con <- url(url_in)
  check <-
    suppressWarnings(try(open.connection(con, open = "rt", timeout = t), silent = TRUE)
                     [1])
  suppressWarnings(try(close.connection(con), silent = TRUE)
  )
  ifelse(is.null(check), TRUE, FALSE)
}

result <- sapply(urls, url_works) # Write results
```

Result of URL test
```{r results}
result <- as.data.frame(result) # Convert results to data frame

result$Hyperlink <- row.names(result) # Convert row names to column
row.names(result) <- NULL # Remove row names
totals <-
  as.data.frame(table(result$result)) # Count number of TRUE and FALSE cases
totals <-
  totals %>% rename(Status = Var1) %>% mutate(Pct = Freq / sum(Freq) * 100)
totals$Pct <- round(totals$Pct, digits = 1) # Round percentage for viewing
totals
```

## Citations

### Data
Horton, L. (2018). UK Higher Education Institution Research Data Management Policies, 2009-2016. [Data Collection]. Colchester, Essex: UK Data Archive. https://doi.org/10.5255/UKDA-SN-851566

### R packages  
R Core Team. (2018). *R: A Language and Environment for Statistical Computing. R Foundation for Statistical Computing*, https://www.R-project.org/  

Wickham, H. et. al. (2019). Welcome to the {tidyverse}, *Journal of Open Source Software, 4*(43), 1686. https://doi.org/10.21105/joss.01686

Xie, Y. (2021). knitr: A General-Purpose Package for Dynamic Report Generation in R, *R package version 1.31*, https://yihui.org/knitr/

```{r citations, include = FALSE}
toBibtex(citation("base"))
toBibtex(citation("tidyverse"))
toBibtex(citation("rmarkdown"))
```
